Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-22 BN_discretizer_paper.tex
modify graphs
Change all plots from probability to probability density
Add appendix

Forward sampling is often used to draw samples from the joint distribution represented by a Bayesian network.
Variables are sampled in topological order such that parental instantiations are always known~\citep{algo_2009}.
Furthermore, the parent $\rightarrow$ child sampling order can be reversed if the marginal probability of the child variable is known.
% By Bayes' rule,

@@

\begin{equation}
\label{eq:opt_prob}
\begin{aligned}
  & \sum_{i=1}^{k-1}
   - \ln
    \paren{
      1 - \exp
      \paren{
        - L \cdot  \frac{
                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
                       }{
                         \cx_n - \cx_1
                        }
      }
    }
      + \sum_{i=1}^{k}
      L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} \\
  & \sum_{i=1}^{k} \brock{
  \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
  +{ \ln \paren{
        \frac{
          {\gamma_i}!
        }{
          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_P}}!
        }
      }}
  } \\
  & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
  { \ln
          {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
    +
    \ln \paren{ {
          \frac{
            {n^{(j)}_{i,l}}!
          }{
            {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
          }
        }
        } }
\end{aligned}
\end{equation}

@@

After prediscretization, the one-variable discretization method is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
Reverse topological order has the advantage of relying on fewer prediscretizations of the continuous variables during the first pass.
For example, in the right-hand graph of Figure~\ref{fig:example_networks}, assume $S_2$ is the only discrete variable.
The discretization of $P_1$ involves both $P_2$ and $\cX$, whereas the discretization of $C_1$ only involves $\cX$.

@@

Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under \num{10}-fold cross validation of the discrete Bayesian network resulting from each discretization method.
The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest likelihood.
The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.

@@

\subsubsection{Discretization while Learning Structure}
\label{subsubsec:auto_exp2}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% WINE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Dataset 2: Wine}
\label{subsec:wine}

@@

\begin{figure}[ht]
  \centering
  \input{graph_wine_exp2_distr_5_11}
  \caption{
    The discretization policy for variables $E$ and $K$ on the learned network.
    The discretization edge $E = 17.9$ also appears in the policies for the fixed network.
  }
  \label{fig:wine_exp2_distr}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Housing
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Data 3: Housing}
\label{subsec:housing}

@@

% \section*{Appendix}

% \begin{algorithm}
%   \caption{ Calculation of $h(u,v)$ for all $u \leq v$}
%   \label{alg:h}
%   \begin{algorithmic}[1]
%   \State Initialize $H$ as an $N \times N$ matrix such that all elements are 0.
%   \State $count_p$ is an $N \times N \times \|\Pa_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pa_X$. This matrix can be calculated in $O(\|\Pa_X\| \cdot N^2)$
%   \For {$u = 1$ to $N$}
%     \For {$v = u$ to $N$}
%       \State $H(u,v) \leftarrow H(u,v) + \ln((v-u + J_p)!) - \ln((J_p -1)!)$
%       \For {$w = 1$ to $\|\Pa_X\|$}
%         \State $H(u,v) \leftarrow H(u,v) - \ln( count_p(u,v,w)!)$
%       \EndFor
%     \EndFor
%   \EndFor
%   \For {$j = 1$ to $n_c$}
%     \State \todo{XXX}
%   \EndFor
%   \end{algorithmic}
% \end{algorithm}

\end{document}
% end of file template.tex

>>>>

Forward sampling is often used to draw samples from the joint distribution represented by a Bayesian network.
Variables are sampled in topological order such that parental instantiations are always known~\citep{PGM_2009}.
Furthermore, the parent $\rightarrow$ child sampling order can be reversed if the marginal probability of the child variable is known.
% By Bayes' rule,

@@

\begin{equation}
\label{eq:opt_prob}
\begin{aligned}
  & \sum_{i=1}^{k-1}
   - \ln
    \paren{
      1 - \exp
      \paren{
        - L \cdot  \frac{
                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
                       }{
                         \cx_n - \cx_1
                        }
      }
    }
      + \sum_{i=1}^{k}
      L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} + \\
  & \sum_{i=1}^{k} \brock{
  \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
  +{ \ln \paren{
        \frac{
          {\gamma_i}!
        }{
          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_P}}!
        }
      }}
  } \\
  & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
  { \ln
          {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
    +
    \ln \paren{ {
          \frac{
            {n^{(j)}_{i,l}}!
          }{
            {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
          }
        }
        } }
\end{aligned}
\end{equation}

@@

After prediscretization, the one-variable discretization method is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
Reverse topological order has the advantage of relying on fewer prediscretizations of the continuous variables during the first pass.
For example, in the right-hand graph of Figure~\ref{fig:example_networks}, assume $S_2$ is the only discrete variable.
The discretization of $P_1$ involves both $P_2$ and $X$, whereas the discretization of $C_1$ only involves $X$.

\begin{figure}[ht]
 \centering
     \input{graph2_right}
  \caption{An example network}
   \label{fig:example_networks}
\end{figure}

@@

Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under \num{10}-fold cross validation of the discrete Bayesian network resulting from each discretization method.
The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest likelihood.
\todo{The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.} \yichun{Mykel has rephrased it?}. On the other hand, there is a netowrk structure where the MDL has a comparable result with the Bayesian method. Please refer to Appendix.

@@

%\subsubsection{Discretization while Learning Structure}
\label{subsubsec:auto_exp2}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% WINE
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\subsection{Dataset 2: Wine}
\label{subsec:wine}

@@

\begin{figure}[ht]
  \centering
  \input{graph_wine_exp2_distr_5_11}
  \caption{
    The discretization policy for variables $E$ and $K$ on the learned network.
    The discretization edge $E = 17.9$ also appears in the policies for the fixed network.
  }
  \label{fig:wine_exp2_distr}
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Housing
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\subsection{Data 3: Housing}
\label{subsec:housing}

@@

\section*{Appendix}
\label{sec:appendix}

The following Bayesian network structure in Figure \ref{fig:auto_graph_3} and the discretization results in Table \ref{table:auto_disc_table_3} demonstrate that the MDL method does not always return smaller number of discretization intervals than the Bayesian approach and also the MDL method can return a comparable result in terms of likelihood. The Bayesian network in Figure \ref{fig:auto_graph_3} is obtained by running Algorithm \ref{alg:structure_learn} fifty times with $u_{\text{parent}} = 2$. Therefore, the network can be considered well-structured, since the \todo{to be continued}.
Many edges appears in both discretization results, as the bold numbers in Table \ref{table:auto_disc_table_3}. 
\begin{figure}[ht]
  \centering
  \scalebox{0.8}{
   \input{graph_autocar_3}}
   \caption{A Bayesian network structure for Auto MPG dataset that leads to a comparable discretization result of the MDL method with the Bayesian method}
  \label{fig:auto_graph_3}
\end{figure}

\begin{table}[h]
  \centering
  \caption{
    Results from discretization of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_3}.
    The first five rows list the discretization edges for each continuous variable.
    The last row lists the mean cross-validated log-likelihood; positive values are better.
    The MDL method does not produce any discretization edges.
  }
\input{table_autoMPG_3.tex}
  \label{table:auto_disc_table_3}
\end{table}
\end{document}
% end of file template.tex

### 2015-11-22 probability_plot_old/graph_auto_exp1_distr_1_3_old.tex
Add appendix

	\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        ylabel=probability density,
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (17.5500,68.0000,0.0000) (17.5500,134.5000,0.0000) (9.0000,134.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,134.5000,0.0010) (17.5500,134.5000,0.0010) (17.5500,159.5000,0.0010) (9.0000,159.5000,0.0010)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0010) (17.5500,159.5000,0.0010) (17.5500,169.5000,0.0010) (9.0000,169.5000,0.0010)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,169.5000,0.0395) (17.5500,169.5000,0.0395) (17.5500,259.0000,0.0395) (9.0000,259.0000,0.0395)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0045) (17.5500,259.0000,0.0045) (17.5500,264.5000,0.0045) (9.0000,264.5000,0.0045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,264.5000,0.2220) (17.5500,264.5000,0.2220) (17.5500,455.0000,0.2220) (9.0000,455.0000,0.2220)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,68.0000,0.0765) (23.9500,68.0000,0.0765) (23.9500,134.5000,0.0765) (17.5500,134.5000,0.0765)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,134.5000,0.0260) (23.9500,134.5000,0.0260) (23.9500,159.5000,0.0260) (17.5500,159.5000,0.0260)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,159.5000,0.0085) (23.9500,159.5000,0.0085) (23.9500,169.5000,0.0085) (17.5500,169.5000,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,169.5000,0.1225) (23.9500,169.5000,0.1225) (23.9500,259.0000,0.1225) (17.5500,259.0000,0.1225)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,259.0000,0.0070) (23.9500,259.0000,0.0070) (23.9500,264.5000,0.0070) (17.5500,264.5000,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,264.5000,0.0355) (23.9500,264.5000,0.0355) (23.9500,455.0000,0.0355) (17.5500,455.0000,0.0355)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,68.0000,0.3525) (46.6000,68.0000,0.3525) (46.6000,134.5000,0.3525) (23.9500,134.5000,0.3525)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,134.5000,0.0770) (46.6000,134.5000,0.0770) (46.6000,159.5000,0.0770) (23.9500,159.5000,0.0770)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,159.5000,0.0020) (46.6000,159.5000,0.0020) (46.6000,169.5000,0.0020) (23.9500,169.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,169.5000,0.0210) (46.6000,169.5000,0.0210) (46.6000,259.0000,0.0210) (23.9500,259.0000,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,264.5000,0.0000) (23.9500,264.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,264.5000,0.0035) (46.6000,264.5000,0.0035) (46.6000,455.0000,0.0035) (23.9500,455.0000,0.0035)};

			\addplot3[mark=+, draw=none, mark size=1.0] coordinates {

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=A,
			ylabel=C,
			colorbar,
			point meta min=0, point meta max=1.2,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.24,...,1.3},
			        ylabel={probability density $\times 10^3$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000-0.1,0.000000) (15.2500,68.0000-0.1,0.000000) (15.2500,70.5000,0.000000) (9.0000,70.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.000000) (15.2500,70.5000,0.000000) (15.2500,93.5000,0.000000) (9.0000,93.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.000000) (15.2500,93.5000,0.000000) (15.2500,109.0000,0.000000) (9.0000,109.0000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.006337) (15.2500,109.0000,0.006337) (15.2500,159.5000,0.006337) (9.0000,159.5000,0.006337)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.037789) (15.2500,159.5000,0.037789) (15.2500,259.0000,0.037789) (9.0000,259.0000,0.037789)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.018824) (15.2500,259.0000,0.018824) (15.2500,284.5000,0.018824) (9.0000,284.5000,0.018824)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.126217) (15.2500,284.5000,0.126217) (15.2500,455.0000,0.126217) (9.0000,455.0000,0.126217)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000-0.1,0.000000) (17.6500,68.0000-0.1,0.000000) (17.6500,70.5000,0.000000) (15.2500,70.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.000000) (17.6500,70.5000,0.000000) (17.6500,93.5000,0.000000) (15.2500,93.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.000000) (17.6500,93.5000,0.000000) (17.6500,109.0000,0.000000) (15.2500,109.0000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.016502) (17.6500,109.0000,0.016502) (17.6500,159.5000,0.016502) (15.2500,159.5000,0.016502)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.096315) (17.6500,159.5000,0.096315) (17.6500,259.0000,0.096315) (15.2500,259.0000,0.096315)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.049020) (17.6500,259.0000,0.049020) (17.6500,284.5000,0.049020) (15.2500,284.5000,0.049020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.152737) (17.6500,284.5000,0.152737) (17.6500,455.0000,0.152737) (15.2500,455.0000,0.152737)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000-0.1,0.000000) (20.9000,68.0000-0.1,0.000000) (20.9000,70.5000,0.000000) (17.6500,70.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.000000) (20.9000,70.5000,0.000000) (20.9000,93.5000,0.000000) (17.6500,93.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.138958) (20.9000,93.5000,0.138958) (20.9000,109.0000,0.138958) (17.6500,109.0000,0.138958)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.261995) (20.9000,109.0000,0.261995) (20.9000,159.5000,0.261995) (17.6500,159.5000,0.261995)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.272130) (20.9000,159.5000,0.272130) (20.9000,259.0000,0.272130) (17.6500,259.0000,0.272130)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.114630) (20.9000,259.0000,0.114630) (20.9000,284.5000,0.114630) (17.6500,284.5000,0.114630)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.040605) (20.9000,284.5000,0.040605) (20.9000,455.0000,0.040605) (17.6500,455.0000,0.040605)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000-0.1,0.126316) (25.6500,68.0000-0.1,0.126316) (25.6500,70.5000,0.126316) (20.9000,70.5000,0.126316)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.054920) (25.6500,70.5000,0.054920) (25.6500,93.5000,0.054920) (20.9000,93.5000,0.054920)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.434635) (25.6500,93.5000,0.434635) (25.6500,109.0000,0.434635) (20.9000,109.0000,0.434635)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.393955) (25.6500,109.0000,0.393955) (25.6500,159.5000,0.393955) (20.9000,159.5000,0.393955)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.096271) (25.6500,159.5000,0.096271) (25.6500,259.0000,0.096271) (20.9000,259.0000,0.096271)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.000000) (25.6500,259.0000,0.000000) (25.6500,284.5000,0.000000) (20.9000,284.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.008643) (25.6500,284.5000,0.008643) (25.6500,455.0000,0.008643) (20.9000,455.0000,0.008643)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000-0.1,0.676923) (28.9000,68.0000-0.1,0.676923) (28.9000,70.5000,0.676923) (25.6500,70.5000,0.676923)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.147157) (28.9000,70.5000,0.147157) (28.9000,93.5000,0.147157) (25.6500,93.5000,0.147157)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.744417) (28.9000,93.5000,0.744417) (28.9000,109.0000,0.744417) (25.6500,109.0000,0.744417)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.332064) (28.9000,109.0000,0.332064) (28.9000,159.5000,0.332064) (25.6500,159.5000,0.332064)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.051024) (28.9000,159.5000,0.051024) (28.9000,259.0000,0.051024) (25.6500,259.0000,0.051024)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.000000) (28.9000,259.0000,0.000000) (28.9000,284.5000,0.000000) (25.6500,284.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.006316) (28.9000,284.5000,0.006316) (28.9000,455.0000,0.006316) (25.6500,455.0000,0.006316)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000-0.1,0.067797) (46.6000,68.0000-0.1,0.067797) (46.6000,70.5000,0.067797) (28.9000,70.5000,0.067797)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.244412) (46.6000,70.5000,0.244412) (46.6000,93.5000,0.244412) (28.9000,93.5000,0.244412)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.313468) (46.6000,93.5000,0.313468) (46.6000,109.0000,0.313468) (28.9000,109.0000,0.313468)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.067685) (46.6000,109.0000,0.067685) (46.6000,159.5000,0.067685) (28.9000,159.5000,0.067685)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.006814) (46.6000,159.5000,0.006814) (46.6000,259.0000,0.006814) (28.9000,259.0000,0.006814)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.000000) (46.6000,259.0000,0.000000) (46.6000,284.5000,0.000000) (28.9000,284.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.000166) (46.6000,284.5000,0.000166) (46.6000,455.0000,0.000166) (28.9000,455.0000,0.000166)};

			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
